\section{Assumptions Ledger}
\begin{itemize}
  \item \textbf{Axioms footprint.} No project axioms: there are no \texttt{axiom}/\texttt{constant} declarations in ERURH. Lean kernel axioms still appear in \texttt{\#print axioms} (e.g., \texttt{propext}, \texttt{Classical.choice}, \texttt{Quot.sound}, \texttt{Lean.ofReduceBool}, \texttt{Lean.trustCompiler}).
  \item \textbf{A/B/C (analytic packages).} The analytic inputs used by Plan~B:
  spectral decay (A), large-sieve bounds (B), and the uniform RMS tail bound (C)
  recorded in Theorem~\ref{thm:C}. These feed the A2 derivation
  (Lemma~\ref{lem:a2-from-abc}).
  \item \textbf{Route B bridges (primary + alternative).} We maintain two analytic
  bridges for Route~B, both exported in \texttt{lean\_gap\_statements.txt}:
  \begin{itemize}
    \item \textbf{Fixed-window bridge (primary route).} The hypothesis
    \texttt{ERURH.Alpha.ModeThresholdControlOnCtxRealWindowFamily} (Assumption
    \ref{assm:threshold-control}) pairs with gate-verified constraints on
    \texttt{ctx\_real}. The paper provides a proof outline; a full proof is
    deferred to a supplement.
    \item \textbf{Buchstab bridge (alternative).} The hypotheses
    \texttt{ERURH.A1\_from\_supercritical\_buchstab} and
    \texttt{ERURH.ExplicitBRhoExpression} are discharged by Lemmas
    \ref{lem:a1-from-supercritical-buchstab} and \ref{lem:buchstab-coefficient}.
  \end{itemize}
  These bridges do not replace the classical A/B/C assumptions; they supply the
  A1/A2 inputs needed for the RMS-local contradiction.
  \item \textbf{Classical / citable.} Zeta explicit-formula setup and classical implications (including the ERU inertia $\leftrightarrow$ $E$-bound links and RH $\Rightarrow$ $E$-bounds). The zero-parameterization objects $\beta,\gamma$ and coefficients $b_\rho$ remain part of this classical package.
  \item \textbf{Gate + certificates (alpha + RMS + beta).} The alpha certificates and RMS coverage are discharged by the reproducible pipeline (\texttt{verify\_gate.py}), which regenerates the rational bounds and certificate values and checks the Lean build. RMS A2-low/A2-tail are generated from frozen \texttt{rms\_context.json} via \texttt{tools/make\_rms\_context.py}. The beta inertia bundle is generated from frozen JSON via \texttt{tools/make\_beta\_certificate.py} and is discharged in the same gate.
\end{itemize}

\subsection*{AxiomsShimAccepted field map (explicit statements)}

\paragraph{alphaInterfacesBase.}
Statement: existence of the alpha interface package (`AlphaInterfaces`) providing
the ERU observable $\log R$ and $J_{\mathrm{rel}}$ in the explicit-formula framework.
Reference/proof: Assumption~\ref{assm:explicit}. Lean field:
\texttt{AxiomsShimAccepted.alphaInterfacesBase}.

\paragraph{explicit\_alpha\_via\_stages.}
Statement: the explicit-formula laws used by the alpha bridge hold, i.e.
`ExplicitFormulaLaws alphaBridge xiAlpha AlphaPsi`.
Reference/proof: Assumption~\ref{assm:explicit}. Lean field:
\texttt{AxiomsShimAccepted.explicit\_alpha\_via\_stages}.

\paragraph{xi\_bounds\_alpha.}
Statement: the $\xi_\alpha$ bounds required by the ERU explicit-formula package
hold (the proposition \texttt{xi\_bounds\_alpha}).
Reference/proof: assumed as part of the explicit-formula bounds package;
to be cited in the explicit-formula bounds section. Lean field:
\texttt{AxiomsShimAccepted.xi\_bounds\_alpha}.

\paragraph{h\_xi\_bounds\_alpha.}
Statement: a proof witness of \texttt{xi\_bounds\_alpha}.
Reference/proof: immediate from the previous assumption. Lean field:
\texttt{AxiomsShimAccepted.h\_xi\_bounds\_alpha}.

\paragraph{xi\_argument\_alpha.}
Statement: the $\xi_\alpha$ argument bounds required by ERURH hold
(\texttt{xi\_argument\_alpha}).
Reference/proof: assumed as part of the explicit-formula bounds package;
to be cited in the argument bounds section. Lean field:
\texttt{AxiomsShimAccepted.xi\_argument\_alpha}.

\paragraph{h\_xi\_argument\_alpha.}
Statement: a proof witness of \texttt{xi\_argument\_alpha}.
Reference/proof: immediate from the previous assumption. Lean field:
\texttt{AxiomsShimAccepted.h\_xi\_argument\_alpha}.

\paragraph{xi\_bounds\_alpha\_of\_hypotheses.}
Statement: `xi_bounds_hypotheses_alpha → xi_bounds_alpha`.
Reference/proof: classical/citable implication (explicit-formula bounds package).
Lean field: \texttt{AxiomsShimAccepted.xi\_bounds\_alpha\_of\_hypotheses}.

\paragraph{xi\_argument\_alpha\_of\_hypotheses.}
Statement: `xi_argument_hypotheses_alpha → xi_argument_alpha`.
Reference/proof: classical/citable implication (argument bounds package).
Lean field: \texttt{AxiomsShimAccepted.xi\_argument\_alpha\_of\_hypotheses}.

\paragraph{rh\_from\_E\_alpha\_of\_hypotheses.}
Statement: `(E_bound_strong_alpha ∧ xi_bounds_alpha ∧ xi_argument_alpha ∧
explicit_rect_alpha ∧ Nonempty (ExplicitFormulaLaws alphaBridge xiAlpha AlphaPsi)) →
RHfromE xiAlpha AlphaPsi`.
Reference/proof: classical/citable implications in the ERU explicit-formula framework.
Lean field: \texttt{AxiomsShimAccepted.rh\_from\_E\_alpha\_of\_hypotheses}.

\paragraph{h\_inertia\_to\_E.}
Statement: `InertiaERU_alpha_strong → E_bound_strong_alpha`.
Reference/proof: classical ERU inertia $\Rightarrow$ strong $E$-bound implication.
Lean field: \texttt{AxiomsShimAccepted.h\_inertia\_to\_E}.

\paragraph{h\_inertia\_of\_E.}
Statement: `E_bound_strong_alpha → InertiaERU_alpha_strong`.
Reference/proof: classical strong $E$-bound $\Rightarrow$ ERU inertia implication.
Lean field: \texttt{AxiomsShimAccepted.h\_inertia\_of\_E}.

\paragraph{h\_RH\_to\_E.}
Statement: `RiemannHypothesis xiAlpha → E_bound_strong_alpha`.
Reference/proof: classical RH $\Rightarrow$ $E$-bound (Assumption~\ref{assm:classical}).
Lean field: \texttt{AxiomsShimAccepted.h\_RH\_to\_E}.
